# Applications

Some _significant_ applications are demonstrated in this chapter.

## Example one

Here is an example using `flashboards` in R (without shiny for now)

```{r, chunk11}
#read and clean data
nyc_inspections <- 
  read_csv("C://Code/Combining-Shiny-R-Markdown/data/DOHMH_New_York_City_Restaurant_Inspection_Results.csv.gz", 
                           col_types = cols(building = col_character()),
                           na = c("NA", "N/A")) %>%
  clean_names() %>%
  filter(grade %in% c("A", "B", "C"),
         boro != "Missing") %>% 
  mutate(inspection_num = row_number(),
         boro = str_to_title(boro)) %>% 
  select(inspection_num, boro, grade, score, critical_flag, cuisine_description)
```

### Grade A Percentage vs Average Score ScatterPlot

```{r, chunk21, message = FALSE, warning = FALSE}
colourCount = length(unique(nyc_inspections$boro))
getPalette = colorRampPalette(brewer.pal(9, "Set2"))

nyc_inspections %>%
  group_by(boro, cuisine_description) %>%
  summarise(aver_score = mean(score),
            num_inspections = n(),
            A_num = sum(grade == "A"),
            A_percent = sum(grade == "A")/n(),
            critaical_percent = sum(grade == "A")/n()) %>%
  mutate(text_label = str_c("Boro: ", boro, '\nCuisine: ', cuisine_description, 
                            '\nnumber of inspection:', num_inspections, '\nnumber of A:', A_num,
                            '\n A%:', paste(round(A_percent*100,digits = 2),"%",sep = "")), 
                            '\n critical%:', paste(round(critaical_percent*100,digits = 2),"%",sep = "")) %>%
  plot_ly(x = ~A_percent, y = ~aver_score, type = "scatter", mode = "markers",   
          alpha = 0.7, color = ~boro, text = ~text_label)


```

### Boxplot of Scores

```{r, chunk31}
colourCount = length(unique(nyc_inspections$boro))
getPalette = colorRampPalette(brewer.pal(9, "Set2"))

cuisine_boxplot <-
  nyc_inspections %>%
  filter(boro == "Manhattan") %>%
  group_by(cuisine_description) %>%
  summarise(num_inspections = n()) %>%
  top_n(5, num_inspections) %>%
  pull(cuisine_description)

nyc_inspections %>%
  filter(boro == "Manhattan",
         cuisine_description %in% cuisine_boxplot) %>%
  plot_ly(y = ~score, color = ~cuisine_description, type = "box", colors = "Set2")
```

### Bar-plot for Average Scores by Cuisine

```{r, chunk41, message = FALSE, warning =FALSE}
nyc_inspections %>%
  group_by(boro, cuisine_description) %>%
  summarise(aver_score = mean(score),
            num_inspections = n(),
            A_num = sum(grade == "A"),
            A_percent = sum(grade == "A")/n(),
            critaical_percent = sum(grade == "A")/n()) %>%
  mutate(text_label = str_c("Boro: ", boro, '\nCuisine: ', cuisine_description, 
                            '\nnumber of inspection:', num_inspections, '\nnumber of A:', A_num,
                            '\n A%:', paste(round(A_percent*100, digits = 2),"%",sep = "")), 
                            '\n critical%:', paste(round(critaical_percent*100, digits = 2),"%",sep = "")) %>%
  filter(boro == "Manhattan") %>%
  plot_ly(x = ~cuisine_description, y = ~aver_score, color = ~cuisine_description, type = "bar", text = ~text_label) %>%
  layout(showlegend = FALSE)
```


## Example two

[still coming]


## Flashboard examples


## Shiny showcases

This is a collection of Shiny examples. You can see them in action on http://gallery.shinyapps.io/example-name where example-name is the directory name of an example here, e.g. http://gallery.shinyapps.io/001-hello

To run the examples locally, you can install the shiny package in R, and use the function runGithub(). For example, to run the example 001-hello:

```{r}
# if (!require('shiny')) install.packages("shiny")
# shiny::runGitHub("shiny-examples", "rstudio", subdir = "001-hello")
# Or you can clone or download this repository, and use run shiny::runApp("001-hello").
```

Note the examples listed below depend on the development version of shiny to show some new features under development. Please be cautious that such features may or may not end up in the final release, or they may also change according to the feedback.

